Component response rate variation drives stability in large complex systems

### 2018-05-26 notebook/SI.Rmd
New results for evolutionary output included in SI

```{r, echo = TRUE}
fordist   <- read.csv(file = "sim_results/different_distr/four_distr_rand.csv");
kable(fordist);
```

@@

```{r}
summarise_randmat <- function(tot_res, fea_res){
    sims    <- length(tot_res);
    all_res <- matrix(data = 0, nrow = sims, ncol = 10);
    for(i in 1:sims){
        unstables <- tot_res[[i]][,1] == FALSE & tot_res[[i]][,2] == FALSE;
        stables   <- tot_res[[i]][,1] == TRUE  & tot_res[[i]][,2] == TRUE;
        unstabled <- tot_res[[i]][,1] == TRUE  & tot_res[[i]][,2] == FALSE;
        stabled   <- tot_res[[i]][,1] == FALSE & tot_res[[i]][,2] == TRUE;
        non_feas  <- fea_res[[i]][,1] == FALSE & fea_res[[i]][,2] == FALSE;
        feasibl   <- fea_res[[i]][,1] == TRUE  & fea_res[[i]][,2] == TRUE;
        unfeased  <- fea_res[[i]][,1] == TRUE  & fea_res[[i]][,2] == FALSE;
        feased    <- fea_res[[i]][,1] == FALSE & fea_res[[i]][,2] == TRUE;
        foundd    <- tot_res[[i]][,3] == TRUE;
        all_res[i, 1]  <- i + 1;
        all_res[i, 2]  <- sum(unstables);
        all_res[i, 3]  <- sum(stables);
        all_res[i, 4]  <- sum(unstabled);
        all_res[i, 5]  <- sum(stabled);
        all_res[i, 6]  <- sum(non_feas);
        all_res[i, 7]  <- sum(feasibl);
        all_res[i, 8]  <- sum(unfeased);
        all_res[i, 9]  <- sum(feased);
        all_res[i, 10] <- sum(foundd);
    }
    return(all_res);
}
```

@@

```{r, echo = FALSE}
evo_res   <- read.csv(file = "sim_results/evolved/evo_results.csv");
kable(evo_res);
```

The distribution of one of the $\gamma$ vectors at $S = 39$ is shown below (all are available on [GitHub]()).

>>>>

```{r, echo = TRUE}
data(fourdists)
kable(fourdists);
```

@@

```{r}
summarise_randmat_ga <- function(tot_res, fea_res){
    sims    <- length(tot_res);
    all_res <- matrix(data = 0, nrow = sims, ncol = 10);
    for(i in 1:sims){
        unstables <- tot_res[[i]][,1] == FALSE & tot_res[[i]][,2] == FALSE;
        stables   <- tot_res[[i]][,1] == TRUE  & tot_res[[i]][,2] == TRUE;
        unstabled <- tot_res[[i]][,1] == TRUE  & tot_res[[i]][,2] == FALSE;
        stabled   <- tot_res[[i]][,1] == FALSE & tot_res[[i]][,2] == TRUE;
        non_feas  <- fea_res[[i]][,1] == FALSE & fea_res[[i]][,2] == FALSE;
        feasibl   <- fea_res[[i]][,1] == TRUE  & fea_res[[i]][,2] == TRUE;
        unfeased  <- fea_res[[i]][,1] == TRUE  & fea_res[[i]][,2] == FALSE;
        feased    <- fea_res[[i]][,1] == FALSE & fea_res[[i]][,2] == TRUE;
        foundd    <- tot_res[[i]][,3] == TRUE;
        all_res[i, 1]  <- i + 1;
        all_res[i, 2]  <- sum(unstables);
        all_res[i, 3]  <- sum(stables);
        all_res[i, 4]  <- sum(unstabled);
        all_res[i, 5]  <- sum(stabled);
        all_res[i, 6]  <- sum(non_feas);
        all_res[i, 7]  <- sum(feasibl);
        all_res[i, 8]  <- sum(unfeased);
        all_res[i, 9]  <- sum(feased);
        all_res[i, 10] <- sum(foundd);
    }
    return(all_res);
}
```

@@

```{r, echo = FALSE}
data(evo_res);
kable(evo_res);
```

The distribution of one of the $\gamma$ vectors at $S = 39$ is shown below (all are available on [GitHub]()). Distributions of $\gamma$ values in vectors for the highest values of $S$ are shown below. <!--- NOTE: This needs to be updated with the new data --->

```{r}
data(evo_out);
plot_evo_out(evo_out);
```

The distribution of $\gamma$ values found by the genetic algorithm is uniform.
